A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-10-23 manuscript/manuscript.tex
final round of edits before submission to NI and bioRxiv

\subsubsection*{Implementing multi-modal studies}
\label{implementing-multi-modal-studies}

@@

Sub-studies are aggregated in the \emph{sub-study} \emph{specification
table} of a MultiStudy class via a list of \emph{SubStudySpec} objects
in the \emph{add\_sub\_study\_specs} class attribute, in the manner of
data and parameter specifications. A SubStudySpec consists of a name, a
Study class, and a \emph{name map} dictionary\emph{.} The name map
dictionary maps data and parameter specification names from the
namespace of the MultiStudy class to the namespace of the Study class.

Entries in the specification tables of sub-study classes that are not
referenced in the sub study's name map are implicitly mapped to the
MultiStudy namespace in the construction of the MultiStudy class by the
metaclass using the name of the sub-study as a prefix. If the spec is a
derivative then the pipeline constructor used to derive it is also
mapped into the MultiStudy namespace. For example, \emph{derived1} in
\emph{sub\_study2} would be mapped to \emph{sub\_study2\_derived1} along
with the method \emph{sub\_study2\_pipeline1}.

>>>>

\subsubsection*{Implementing multi-modal studies: MultiStudy classes}
\label{implementing-multi-modal-studies}

@@

Sub-studies are aggregated in the \emph{sub-study} \emph{specification
table} of a MultiStudy class via a list of \emph{SubStudySpec} objects
in the \emph{add\_sub\_study\_specs} class attribute in the manner of
data and parameter specifications. A SubStudySpec consists of a name, a
Study class, and a \emph{name map} dictionary\emph{.} The name map
dictionary maps data and parameter specification names from the
sub-study namespace to the namespace of the MultiStudy class.

Entries in the specification tables of sub-study classes that are not
referenced in the sub study's name map are implicitly mapped to the
MultiStudy namespace by the MultiStudyMetaClass during construction of the MultiStudy class,
using the name of the sub-study as a prefix.
If the specification is derived, then its associated pipeline constructor method
is also mapped into the MultiStudy namespace. For example, \emph{derived1} in
\emph{sub\_study2} would be mapped to \emph{sub\_study2\_derived1} along
with the method \emph{sub\_study2\_pipeline1}.
